Choosing a Population Genomics Approach

### 2022-10-26 choosing-population-genetics.Rmd
listing all 3 types of sequencing stretegies for choosing a population genetic sequencing approach

## 2) Reduced-representation sequencing {.unlisted .unnumbered}
As the name suggests, this approach aims to sequence a reduced portion of the genome across multiple individuals at moderate to high coverage for variant discovery and genotyping with high confidence. The genome fragments can be selected at random, or through targeted probe assays. Variations of this type of sequencing approach include...

@@

## 3) Pooled individuals (Poolseq)  {.unlisted .unnumbered}
Sequencing pools of individuals to provide information on genome-wide population allele frequencies (see review in [@futschik2010next]).

>>>>

## 2) Reduced-representation sequencing
As the name suggests, this approach aims to sequence a reduced portion of the genome across multiple individuals at moderate to high coverage for variant discovery and genotyping with high confidence. The genome fragments can be selected at random, or through targeted probe assays. Variations of this type of sequencing approach include...

@@

## 3) Pooled individuals (Poolseq)
Sequencing pools of individuals to provide information on genome-wide population allele frequencies (see review in [@futschik2010next]).
